### 2013-10-22 research/paper/figure/m_star_collapsed.tex
uploaded 22-oct 2013 6.36

\begin{figure}
\setlength{\unitlength}{\textwidth}

  \begin{picture}(1,0.35)(0,0.75)

  \put(0.15,0.76){\includegraphics[width=0.7\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}

 	\put(0.11,0.95){\large $\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

 	 	\put(0.45,0.75){ $c\rho\mathcal{A}U$}

  \end{picture}

>>>>

\begin{figure}

\setlength{\unitlength}{\textwidth}
\fbox{
  \begin{picture}(1,0.3)(0.0,0.45)

       \put(0.025,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}
       \put(0.495,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_noshed_mstar.eps}}

        \put(-0.01,0.637){\large $\frac{P_{m}}{\rho \mathcal{A}U^3}$}

        \put(0.23,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$} 	
        \put(0.73,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$}

     \put(0.085,0.709){\small(a)}
     \put(0.555,0.709){\small(b)}

  \end{picture}
  }
